Parameters estimation via HOSVD

### 2024-10-12 Code/R/Research/HOSVD parameters estimate.Rmd
Minor adjustments

```{r test-1d-esprit-noise}
set.seed(10)
n <- 25
L <- 15
I <- 14; L.tens <- 8
rates.true <- c(-0.01, -0.02)
freqs.true <- c(0.2, 0.22)
signal <- exp((rates.true[1] + 2i * pi * freqs.true[1]) * 0:(n - 1)) +
  exp((rates.true[2] + 2i * pi * freqs.true[2]) * 0:(n - 1))
sd <- 0.025
R <- 1000

pars.ssa <- list(
  rate1 = numeric(R),
  rate2 = numeric(R),
  freq1 = numeric(R),
  freq2 = numeric(R)
)
pars.tssa <- list(
  rate1 = numeric(R),
  rate2 = numeric(R),
  freq1 = numeric(R),
  freq2 = numeric(R)
)
pb <- txtProgressBar(max = R, style = 3)
for (i in seq(R)) {
  noise <- CCSWGN(n, mean = 0, sd = sd)
  x <- signal + noise
  x.ssa <- ssa(x, L = L)
  par.ssa <- parestimate(x.ssa, groups = list(1:2))
  pars.ssa$rate1[i] <- max(par.ssa$rates[1], par.ssa$rates[2])
  pars.ssa$rate2[i] <- min(par.ssa$rates[1], par.ssa$rates[2])
  pars.ssa$freq1[i] <- min(par.ssa$frequencies[1], par.ssa$frequencies[2])
  pars.ssa$freq2[i] <- max(par.ssa$frequencies[1], par.ssa$frequencies[2])
  par.tssa <- tens_esprit(x, I, L.tens, groups = list(1:2), status = FALSE)
  pars.tssa$rate1[i] <- max(par.tssa[[1]]$rates[1], par.tssa[[1]]$rates[2])
  pars.tssa$rate2[i] <- min(par.tssa[[1]]$rates[1], par.tssa[[1]]$rates[2])
  pars.tssa$freq1[i] <- min(par.tssa[[1]]$frequencies[1], par.tssa[[1]]$frequencies[2])
  pars.tssa$freq2[i] <- max(par.tssa[[1]]$frequencies[1], par.tssa[[1]]$frequencies[2])
  setTxtProgressBar(pb, i)
}
close(pb)
cat("Rate 1, SSA: ", rrmse(rates.true[1], pars.ssa$rate1), '\n')
cat("Rate 1, HO-SSA: ", rrmse(rates.true[1], pars.tssa$rate1), '\n')
cat("Rate 2, SSA: ", rrmse(rates.true[2], pars.ssa$rate2), '\n')
cat("Rate 2, HO-SSA: ", rrmse(rates.true[2], pars.tssa$rate2), '\n')
cat("Freq 1, SSA: ", rrmse(freqs.true[1], pars.ssa$freq1), '\n')
cat("Freq 1, HO-SSA: ", rrmse(freqs.true[1], pars.tssa$freq1), '\n')
cat("Freq 2, SSA: ", rrmse(freqs.true[2], pars.ssa$freq2), '\n')
cat("Freq 2, HO-SSA: ", rrmse(freqs.true[2], pars.tssa$freq2), '\n')
```

>>>>

```{r test-1d-esprit-noise, results='hide'}
set.seed(10)
n <- 25
L <- 15
I <- 14; L.tens <- 8
rates.true <- c(-0.01, -0.02)
freqs.true <- c(0.2, 0.22)
signal <- exp((rates.true[1] + 2i * pi * freqs.true[1]) * 0:(n - 1)) +
  exp((rates.true[2] + 2i * pi * freqs.true[2]) * 0:(n - 1))
sd <- 0.04
R <- 1000

pars.ssa <- list(
  rate1 = numeric(R),
  rate2 = numeric(R),
  freq1 = numeric(R),
  freq2 = numeric(R)
)
pars.tssa <- list(
  rate1 = numeric(R),
  rate2 = numeric(R),
  freq1 = numeric(R),
  freq2 = numeric(R)
)
pb <- txtProgressBar(max = R, style = 3)
for (i in seq(R)) {
  noise <- CCSWGN(n, mean = 0, sd = sd)
  x <- signal + noise
  x.ssa <- ssa(x, L = L)
  par.ssa <- parestimate(x.ssa, groups = list(1:2))
  pars.ssa$rate1[i] <- max(par.ssa$rates[1], par.ssa$rates[2])
  pars.ssa$rate2[i] <- min(par.ssa$rates[1], par.ssa$rates[2])
  pars.ssa$freq1[i] <- min(par.ssa$frequencies[1], par.ssa$frequencies[2])
  pars.ssa$freq2[i] <- max(par.ssa$frequencies[1], par.ssa$frequencies[2])
  par.tssa <- tens_esprit(x, I, L.tens, groups = list(1:2), status = FALSE)
  pars.tssa$rate1[i] <- max(par.tssa[[1]]$rates[1], par.tssa[[1]]$rates[2])
  pars.tssa$rate2[i] <- min(par.tssa[[1]]$rates[1], par.tssa[[1]]$rates[2])
  pars.tssa$freq1[i] <- min(par.tssa[[1]]$frequencies[1], par.tssa[[1]]$frequencies[2])
  pars.tssa$freq2[i] <- max(par.tssa[[1]]$frequencies[1], par.tssa[[1]]$frequencies[2])
  setTxtProgressBar(pb, i)
}
close(pb)
```
```{r, results='hold'}
cat("Rate 1, SSA: ", rrmse(rates.true[1], pars.ssa$rate1), '\n')
cat("Rate 1, HO-SSA: ", rrmse(rates.true[1], pars.tssa$rate1), '\n')
cat("Rate 2, SSA: ", rrmse(rates.true[2], pars.ssa$rate2), '\n')
cat("Rate 2, HO-SSA: ", rrmse(rates.true[2], pars.tssa$rate2), '\n')
cat("Freq 1, SSA: ", rrmse(freqs.true[1], pars.ssa$freq1), '\n')
cat("Freq 1, HO-SSA: ", rrmse(freqs.true[1], pars.tssa$freq1), '\n')
cat("Freq 2, SSA: ", rrmse(freqs.true[2], pars.ssa$freq2), '\n')
cat("Freq 2, HO-SSA: ", rrmse(freqs.true[2], pars.tssa$freq2), '\n')
```
